Hybrid platforms and bargaining power

### 2023-03-26 src/paper/application.tex
Add more graphs to results section

>>>>

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$A^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=2.6, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=south east
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=A_bench]{\equilibrium};
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=A]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A_noF]{\equilibrium};
            \legend{Benchmark, Bargaining, Pure retail}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium aggregate as a function of the number of platform products.}
    \label{fig:aggregate_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$\pi_P^{t*}$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=0.65, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=south east
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=pi_P_bench]{\equilibrium};
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=pi_P]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=pi_P_noF]{\equilibrium};
            \legend{Benchmark, Bargaining, Pure retail}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium platform profit as a function of the number of platform products.}
    \label{fig:pi_P_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$F_F$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=0.65, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=north east
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=F_F_opt]{\equilibrium};
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=F_F_implied]{\equilibrium};
            \legend{Benchmark (optimal), Bargaining (implied)}
        \end{axis}
    \end{tikzpicture}
    \caption{Optimal/implied entry fee as a function of the number of platform products.}
    \label{fig:F_F_eq}
\end{figure}
